Details matter: Similar host galaxies can harbor different merging compact binary populations

### 2016-07-11 paper/paper.tex
section 3 comments jillian

%
% RELATED NOTES (Richard)
%    PersonalJBArchive
%    PSnucleosynthesis/Branch-GalaxyAssemblyAndZDistribution 
%        */bhmetals   : paper.tex, paper-shorter.tex
\documentclass[nofootinbib,twocolumn,prd]{emulateapj}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{color}
\usepackage{ifpdf}
%\usepackage{eps2pdf}

@@

\section{Introduction}
% POINT: LIGO soon will detect compact binary mergers....
%     ... and possibly EM counter part too
%     ... which will enable new physics
Gravitational waves have been detected from  coalescing  black hole binaries \citep{DetectionPaper,LIGO-O1-BBH}. 
Over the next few years, ground-based gravitational wave detectors like LIGO 
and Virgo  should detect the gravitational
wave signal from many more similar merging compact binaries \citep{LIGO-O1-BBH,RatesPaper,gwastro-EventPopsynPaper-2016}, as well as  binary  neutron stars and black hole-neutron star binaries \citep{LIGO-Inspiral-Rates,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.
%
The host galaxies of gravitational wave sources will identified, either directly or statistically.  
On the one hand, addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
electromagnetic radiation  via a number of  mechanisms, including a strong but tightly beamed
ultrarelativistic jet and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
\citep[see,e.g.,][and references therein]{2013PhRvL.111r1101C,short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
% People we can't afford the space to cite, alas:
%    - 2015arXiv150101986H   -
%    - 2013MNRAS.430.2121P - Rosswog recent
%    - Shibata group/Koutarou
In addition to providing a wealth of information about the merger event itself, a multimessenger detection will pin down
the sky position and therefore approximate birthplace of each merging binary.    
%
On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \cite{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
networks increase in sensitivity, these localizations will allow statistical and, eventually, unique identification of
host galaxies directly, even without associated electromagnetic emission.
%
As with supernovae and  GRBs, these host galaxy associations   are expected to tightly constrain models for compact binary
formation; see, for comparison,  \citet{2011MNRAS.412.1508M}, \citet{long-grb-GuettaPiran2007},
\citet{2014ARAA..52...43B}, and references therein. %2010ApJ...722.1879M,2010MNRAS.407.1314M}.     
%

@@

\subsection{Simulating galaxy evolution}
To thoroughly study the significance of low metallicity star
formation, we examine cosmological smoothed particle hydrodynamics
(SPH) $N$-body simulations of Milky Way-like galaxies with GASOLINE
\citep{2001PhDT........21S,2004NewA....9..137W}.  These simulations allow us to analyze both
spatially and temporally resolved star formation, and determine not
only the metallicity history of compact object progenitors, but also
their dynamical evolution.  
%maybe move the below section to later and/or consolidate
One simulation we report here, $h258$,
involves the formation of a Milky Way-like disk galaxy whose
progenitors undergo major mergers at $z = 2$ and $z = 0.8$.  This
simulation has been previously discussed by
\citet{2009MNRAS.398..312G,2010ApJ...721L.148B,2011ApJ...742...13B,2011ApJ...728...51B}; however we have
re-run the simulation at a factor of two higher in spatial resolution
and additionally included new physics including a prescription for
cooling by molecular hydrogen \citet{2012MNRAS.425.3058C}.

We selected our simulated region of interest from a 50 Mpc volume of
uniform resolution, and resampled the region at very high
resolution using the volume renormalization technique \citep{1993ApJ...412..455K}.
This technique allows us to follow the detailed physical processes
involved in galaxy evolution in our selected region while still
including large-scale torques from cosmic structure.  We use
WMAP3 cosmology \citep{WMAP} and model the ionizing UV background
with the prescription from \citet{1996ApJ...461...20H}.  Stars form
probabilistically from gas particles which meet density ($n_{min} =
10$ amu cm$^{-3}$) and temperature ($T_{max} = 10^4$ K) thresholds. If a gas
particle meets these criteria, it has a likelihood of forming a star
particle (representing a simple stellar population with a Kroupa IMF
\citep{2001MNRAS.322..231K}) which is given by

@@

\noindent
where the star formation efficiency parameter $c^*$ is set to 0.1 such
that our galaxies match the observed Kennicutt-Schmidt law
\citep{1989ApJ...344..685K};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
particle masses;\footnote{In our high-resolution simulations \textbf{ROS-check!}\jillianremark{this number is correct, is that what you want to check? - JMB}, each gas particle starts with a mass
  $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{2010ApJ...717..121C} for a discussion
of resolution issues in these SPH simulations.} $t_{form}$ is the dynamical time for the gas
particle; and $\Delta t$ is the time between star formation episodes,
which we set to 1 Myr.  We model supernova feedback using the
blastwave formalism described in \citet{1977ApJ...218..148M} and implemented in
our simulations as in \citet{2006MNRAS.373.1074S}.  Each supernova releases
$E_{SN} = 10^{51}$ erg into the surrounding gas with a radius
determined by the blastwave equations.  These particles are not
allowed to cool for the duration of the blastwave, mimicking the
snowplow phase of a supernova explosion.  Previous works have found
that this set of parameters results in realistic galaxies which obey a
number of observed relations such as the mass-metallicity relation
\citep{2007ApJ...655L..17B}, the Tully-Fisher relation \citep{2009MNRAS.398..312G}, and
the size-luminosity relation \citep{2011ApJ...728...51B}, as well as reproduce
the detailed characteristics of bulgeless dwarf galaxies
\citep{2010Natur.463..203G} and the Milky Way \citep{2011ApJ...742...76G}.

Also included in our simulations is a scheme for turbulent metal
diffusion \citep{2010MNRAS.407.1581S}.  Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{1996A&A...315..105R}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.  We follow metal enrichment from both Type II and Type 1a
supernova, with metal yields derived from \citet{1993PhR...227...65W} and
\citet{1986A&A...158...17T} respectively.  From this point onwards metals
diffuse through the surrounding gas, according to 
\begin{equation}
\frac{dZ}{dt}|_{diff} = \nabla (D \nabla {Z}) \\
\end{equation}
%
where the diffusion paremeter $D$ is given by
%
\begin{equation}
D = C_{diff} |S_{ij}| h
\end{equation}
%
and $h$ is the SPH smoothing length, $S_{ij}$ is the trace-free shear
tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.

@@

We identify individual galaxies using the halo finder $AHF$
\citep{2004MNRAS.351..399G,2009ApJS..182..608K}, which identifies halos based on an
overdensity criterion for a flat universe \citep{1997PhDT........14G}.  For this
work, we are focusing on the primary (i.e. most massive) galaxy at any
given redshift, which serves as the progenitor to our $z = 0$ Milky
Way-like galaxy.

@@

The simulation h277 (Boring Galaxy) is a Milky Way analog with a
quiescent merger history.  It experiences its last major merger at $z
= 3$, after which a small number of minor interactions permeate its
life.  This simulation has been shown to emulate several Milky Way
properties, including stellar dynamics
\citep{2012ApJ...758L..23L,2014ApJ...794..151L,2014ApJ...790...89K}, baryon fraction
\citep{2013ApJ...766...56M}, halo properties \citep{2009ApJ...702.1058Z,2010ApJ...721..738Z}, and
disk properties \citep{2011ApJ...728...51B}.  It has a virial mass of $M_{vir} =
6.79 \times 10^{11} \msun$, stellar mass $M_* = 4.24 \times 10^{10}
\msun$, and maximum circular velocity $v_{circ} = 235$ km s$^{-1}$.

  The simulation h258 (Exciting Galaxy), on the other hand, has a much
  more active merger history.  At $z = 1$ there is a 1:1 merger event;
  a gas disk rapidly reforms following the collision (see
  \citet{2009MNRAS.398..312G}), resulting in a massive disk galaxy at $z = 0$
  which looks remarkably similar to the Milky Way and to the other
  simulation, h277.  Prior to the $z = 1$ merger, each of the two
  progenitor galaxies actually experiences its own additional major
  merger events around $z = 2$.  The combination of
  the series of major mergers, plus a number of minor interactions and
  flybys, gives a stark contrast to the relatively quiescent history
  of h277.  At $z = 0$, h258 has a virial mass of $M_{vir} = 7.74
  \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10}
  \msun$, and maximum circular velocity $v_{circ} = 242$ km s$^{-1}$.  \editremark{Might we want to show the images of these galaxies?}

@@

\begin{figure*}
\includegraphics[width=\columnwidth]{Figures/boring}
\includegraphics[width=\columnwidth]{Figures/exciting}
\caption{\textbf{Two fiducial galaxies}
}
\end{figure*}

@@

To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event
detection in an individual galaxy, motivated by
the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals; similar approaches have been used by
\cite{2016arXiv160508783L} and others.

Binary evolution calculations suggest the binary compact object formation rate rate depends sensitively on the assumed metallicity, in conjunction
with other parameters \citep[see,\,e.g.][and references
  therein]{popsyn-LowMetallicityImpact-Chris2008,popsyn-LIGO-SFR-2008,gwastro-EventPopsynPaper-2016}.
% POINT: 
%   - final BH spin, mass can change number favored
%   - of course
Gravitational wave detectors are also far more sensitive to  massive compact binaries, as are  preferentially  formed in low metallicity
environments \citep{PSellipticals,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.  As a result, low metallicity
environments can be overwhelmingly efficient factories for detectable black hole binaries
\citep{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,gwastro-EventPopsynPaper-2016}.  
%
For this reason, our estimates for compact binary coalescence rates must account for how often  different star-forming
conditions occur;  how often compact binaries that can coalesce now can  derive from each environment; and how often LIGO will detect compact
binaries with different masses, all other things being equal.

\begin{widetext}
% POINT:  Model
To characterize how much more likely LIGO will detect coalescing binaries with different masses, we use a common and
naive estimate for the volume to which advanced LIGO is sensitive \citep[see,e.g.,][]{PSellipticals}:\footnote{For
  simplicity, in this calculation we neglect the effects of cosmology; strong field coalescence; and black hole spin;
  see \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, \cite{AstroPaper}, or \cite{RatesPaper} for more details.}
\begin{eqnarray}
V = \frac{4\pi}{3} [445 \unit{Mpc}]^3 \int p(m_1,m_2|Z) dm_1 dm_2 [ (\mc/1.2 M_\odot)^{5/6}]^3
\end{eqnarray}
where $\mc\equiv (m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$.   
This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
mergers, through the characteristic chirp mass $\mc_{*}(Z)\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
  M_\odot)^{15/6}]^{5/16}$ .  We calibrate our metallicity-dependent mass distributions to metallicity-dependent binary
evolution calculations presented in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} and
\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; see, e.g., their Table 1 and Figures 5-7.    For neutron
stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.  For BH-NS binaries, we adopt a
highly simplified model: the black hole masses are uniformly \editremark{fixme?} drawn from $5 M_\odot$ to the maximum
black hole mass $M_{max}(Z)$ allowed by
\emph{isolated} stellar evolution, as reported in prior work \citep[see,e.g.][and references
  therein]{gwastro-EventPopsynPaper-2016}.  In agreement with much more detailed prior work \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, this simplified model yields typical chirp masses for BH-NS binaries that
vary slightly as $Z/Z_\odot$ decreases, from a lower limit of $3 M_\odot$ near solar metallicity to an upper limit of
$4.3 M_\odot$ in low-metallicity environments.  Finally, for binary black holes, we assume  comparable-mass binaries
form ($m_1=m_2$), with the distribution of component masses chosen to be $\propto m_1^{-p}$ 
 with $p=2$ between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise; see, e.g.,
\cite{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.    For binary black holes, this means  the
detection-weighted mass distribution [$\propto p(m_1,m_2)
\mc^{15/6}$] depends weakly on mass [$ p(m_1,m_2)
\mc^{15/6} \propto m_1^{-0.5} \delta(m_1-m_2)$.  In our simple model, the total  and chirp mass
distributions   are qualitatively consistent with detailed  binary evolution calculations \citep{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.

@@

% POINT:  Model
To characterize how often different star-forming conditions occur, we use our simulations, which provide a galaxy's star formation rate
$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$.

% POINT: 
To characterize how often compact binaries form and coalesce, we use the ansatz adopted in \abbrvPSellipticals{} and
\abbrvPSgrb{}: for a star-forming parcel of mass $\Delta M$ the number of binaries born at time $0$ which
are coalescing now is $\lambda \Delta M dP/dt$, where $\lambda$ is an overall efficiency per unit mass and $P(<t|Z)$ is
a metallicity-dependent delay time distribution.\footnote{For simplicity, we assume the mass and delay time
  distributions are uncorrelated.  Figure A9 in \abbrvPSgrb{} shows this approximation, while not strictly true, is an
  excellent approximation for merging BH-BH binaries at solar metallicity.  }
    In this paper we only investigate the relative contribution of
different star-forming environments, not the overall normalization, so the overall scale of $\lambda$ is irrelevant.  
However, to account for the strong tendency of low-metallicity star-forming regions to produce many binary compact
objects, we adopt a power law
\begin{eqnarray}
\label{eq:LambdaVersusZModel}
\lambda(Z) &=& \lambda_o \text{max}[(Z/Z_\odot)^{-a}, F_{max}] 
\end{eqnarray}
with $a\in [0,3]$ and $F_{max}<10^3$
%$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
 (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).  For the purposes of illustration, we adop a  concrete scale
factor  $
\lambda_0 = 10^{-3}/M_\odot $,  a typical value suitable for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
%
For binaries containing neutron stars, for simplicity and without loss of generality we adopt the universal delay time distribution
%% Finally, we parameterize the delay time distribution by  either
%% \begin{eqnarray}
%% P_t(<t) &=& \begin{cases}
%% 0 & t<10 \unit{Myr} \\
%% (t/13\unit{Gyr})^{b}& t \in [10\unit{Myr},t_H]
%% \end{cases} 
%% \end{eqnarray}
%% with $b> 0$ or as the special case
\begin{eqnarray}
\frac{dP_t(<t)}{dt} =  \begin{cases}
0 & t<10 \unit{Myr} \\
\frac{1}{t \ln (13 \unit{Gyr}/10\unit{Myr})} & t \in [10\unit{Myr},13\unit{Gyr}]
\end{cases} 
\end{eqnarray}
\abbrvPSgrb{} and \abbrvPSellipticals{} show this distribution is reasonable approximations to compact binary delay
time distributions.\footnote{Simulations suggest the delay time distribution varies from model to model and with mass.
  These variations have less impact on our results than the evolving metallicity distribution of star forming gas.}
%
For suitable choices of parameter, our phenomenological response function is qualitatively consistent with the results of detailed simulations of binary
evolution  \citep{2010ApJ...715L.138B,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2-StarTrackRevised-2012}.

For binary black holes formed near solar metallicity, the delay time distribution can favor long delays between birth
and merger, as demonstrated in Figures 9 and 10 of \abbrvPSellipticals{}.  [Figure 2 of  \cite{2016arXiv160508783L} is
  an extreme example of this well-known trend.]  In practice, however, binary black holes produced near solar
metallicity correspond to a relatively small proportion of the overall population; we therefore neglect this
effect \footnote{may want to change}.

>>>>

%
% RELATED NOTES (Richard)
%    PersonalJBArchive
%    PSnucleosynthesis/Branch-GalaxyAssemblyAndZDistribution 
%        */bhmetals   : paper.tex, paper-shorter.tex
\documentclass[nofootinbib,twocolumn,prd]{emulateapj}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{color}
\usepackage{ifpdf}
\usepackage[normalem]{ulem}
%\usepackage{eps2pdf}

@@

\section{Introduction}
% POINT: LIGO soon will detect compact binary mergers....
%     ... and possibly EM counter part too
%     ... which will enable new physics
Gravitational waves have been detected from  coalescing  black hole binaries \citep{DetectionPaper,LIGO-O1-BBH}. 
Over the next few years, ground-based gravitational wave detectors like LIGO 
and Virgo  should detect the gravitational
wave signal from many more similar merging compact binaries \citep{LIGO-O1-BBH,RatesPaper,gwastro-EventPopsynPaper-2016}, as well as  binary  neutron stars and black hole-neutron star binaries \citep{LIGO-Inspiral-Rates,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.
%
The host galaxies of gravitational wave sources will be identified, either directly or statistically.  
On the one hand, addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
electromagnetic radiation  via a number of  mechanisms, including a strong but tightly beamed
ultrarelativistic jet and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
\citep[see,e.g.,][and references therein]{2013PhRvL.111r1101C,short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
% People we can't afford the space to cite, alas:
%    - 2015arXiv150101986H   -
%    - 2013MNRAS.430.2121P - Rosswog recent
%    - Shibata group/Koutarou
In addition to providing a wealth of information about the merger event itself, a multimessenger detection will pin down
the sky position and therefore approximate birthplace of each merging binary.    
%
On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \cite{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
networks increase in sensitivity, these localizations will allow statistical and, eventually, unique identification of
host galaxies directly, even without associated electromagnetic emission.
%
As with supernovae and  GRBs, these host galaxy associations   are expected to tightly constrain models for compact binary
formation; see, for comparison,  \citet{2011MNRAS.412.1508M}, \citet{long-grb-GuettaPiran2007},
\citet{2014ARAA..52...43B}, and references therein. %2010ApJ...722.1879M,2010MNRAS.407.1314M}.     
%

@@

\subsection{Simulating galaxy evolution}
To thoroughly study the significance of low metallicity star
formation, we examine cosmological smoothed particle hydrodynamics
(SPH) $N$-body simulations of Milky Way-like galaxies with GASOLINE
\citep{Stadel01,Wadsley04}.  These simulations allow us to analyze both
spatially and temporally resolved star formation, and determine not
only the metallicity history of compact object progenitors, but also
their dynamical evolution.  
%maybe move the below section to later and/or consolidate
One simulation we report here, $h258$,
involves the formation of a Milky Way-like disk galaxy whose
progenitors undergo major mergers at $z = 2$ and $z = 0.8$.  This
simulation has been previously discussed by
\citet{Governato09,Bellovary10,Bellovary11,Brooks11}; however we have
re-run the simulation at a factor of two higher in spatial resolution
and additionally included new physics including a prescription for
cooling by molecular hydrogen \citet{Christensen12}.

We selected our simulated region of interest from a 50 Mpc volume of
uniform resolution, and resampled the region at very high
resolution using the volume renormalization technique \citep{Katz93}.
This technique allows us to follow the detailed physical processes
involved in galaxy evolution in our selected region while still
including large-scale torques from cosmic structure.  We use
WMAP3 cosmology \citep{WMAP} and model the ionizing UV background
with the prescription from \citet{Haardt96}.  Stars form
probabilistically from gas particles which meet density ($n_{min} =
10$ amu cm$^{-3}$) and temperature ($T_{max} = 10^4$ K) thresholds. If a gas
particle meets these criteria, it has a likelihood of forming a star
particle (representing a simple stellar population with a Kroupa IMF
\citep{Kroupa01}) which is given by

@@

\noindent
where the star formation efficiency parameter $c^*$ is set to 0.1 such
that our galaxies match the observed Kennicutt-Schmidt law
\citep{1989ApJ...344..685K};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
particle masses;\footnote{In our high-resolution simulations \textbf{ROS-check!}\jillianremark{this number is correct, is that what you want to check? - JMB}, each gas particle starts with a mass
  $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{2010ApJ...717..121C} for a discussion
of resolution issues in these SPH simulations.} $t_{form}$ is the dynamical time for the gas
particle; and $\Delta t$ is the time between star formation episodes,
which we set to 1 Myr.  We model supernova feedback using the
blastwave formalism described in \citet{1977ApJ...218..148M} and implemented in
our simulations as in \citet{Stinson06}.  Each supernova releases
$E_{SN} = 10^{51}$ erg into the surrounding gas with a radius
determined by the blastwave equations.  These particles are not
allowed to cool for the duration of the blastwave, mimicking the
snowplow phase of a supernova explosion.  Previous works have found
that this set of parameters results in realistic galaxies which obey a
number of observed relations such as the mass-metallicity relation
\citep{Brooks07}, the Tully-Fisher relation \citep{Governato09}, and
the size-luminosity relation \citep{Brooks11}, as well as reproduce
the detailed characteristics of bulgeless dwarf galaxies
\citep{Governato10} and the Milky Way \citep{2011ApJ...742...76G}.

Also included in our simulations is a scheme for turbulent metal
diffusion \citep{Shen10}.  Metals are created in supernova explosions
and deposited directly to the gas within the blast radius.  Stellar
masses are converted to ages as described by \citet{1996A&A...315..105R}, and
stars more massive than 8 M$_\odot$ are able to undergo a Type II
supernova.  We follow metal enrichment from both Type II and Type 1a
supernova, with metal yields derived from \citet{Weaver93} and
\citet{Thielemann86} respectively.  From this point onwards metals
diffuse through the surrounding gas, according to 
\begin{equation}
\frac{dZ}{dt}|_{diff} = \nabla (D \nabla {Z}) \\
\end{equation}
%
where the diffusion parameter $D$ is given by
%
\begin{equation}
D = C_{diff} |S_{ij}| h
\end{equation}
%
and $h$ is the SPH smoothing length, $S_{ij}$ is the trace-free shear
tensor, and $C_{diff}$ is a dimensionless constant which we set to a conservative value of 0.03.

@@

We identify individual galaxies using the halo finder $AHF$
\citep{Gill04,Knollman09}, which identifies halos based on an
overdensity criterion for a flat universe \citep{Gross97}.  For this
work, we are focusing on the primary (i.e. most massive) galaxy at any
given redshift, which serves as the progenitor to our $z = 0$ Milky
Way-like galaxy.

@@

The simulation h277 (Boring Galaxy) is a Milky Way analog with a
quiescent merger history.  It experiences its last major merger at $z
= 3$, after which a small number of minor interactions permeate its
life.  This simulation has been shown to emulate several Milky Way
properties, including stellar dynamics
\citep{Loebman12,Loebman14,2014ApJ...790...89K}, baryon fraction
\citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10}, and
disk properties \citep{Brooks11}.  It has a virial mass of $M_{vir} =
6.79 \times 10^{11} \msun$, stellar mass $M_* = 4.24 \times 10^{10}
\msun$, and maximum circular velocity $v_{circ} = 235$ km s$^{-1}$.

  The simulation h258 (Exciting Galaxy), on the other hand, has a much
  more active merger history.  At $z = 1$ there is a 1:1 merger event;
  a gas disk rapidly reforms following the collision (see
  \citet{Governato09}), resulting in a massive disk galaxy at $z = 0$
  which looks remarkably similar to the Milky Way and to the other
  simulation, h277.  Prior to the $z = 1$ merger, each of the two
  progenitor galaxies actually experiences its own additional major
  merger events around $z = 2$.  The combination of
  the series of major mergers, plus a number of minor interactions and
  flybys, gives a stark contrast to the relatively quiescent history
  of h277.  At $z = 0$, h258 has a virial mass of $M_{vir} = 7.74
  \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10}
  \msun$, and maximum circular velocity $v_{circ} = 242$ km s$^{-1}$.  \editremark{Might we want to show the images of these galaxies?}

@@

\begin{figure*}
\includegraphics[width=\columnwidth]{Figures/boring}
\includegraphics[width=\columnwidth]{Figures/exciting}
\caption{Synthetic SDSS $gri$ images of our two Milky Way-type galaxies, h277 (left) and h258 (right), created with \textsc{SUNRISE} \citep{Jonsson06}.
\label{fig:images}
}
\end{figure*}

@@

To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event
detection in an individual galaxy, motivated by
the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals; \jillianremark{this is first mention of PSG and PSE, define} similar approaches have been used by
\cite{2016arXiv160508783L} and others.

Binary evolution calculations suggest the binary compact object formation rate rate depends sensitively on the assumed metallicity, in conjunction
with other parameters \citep[see,\,e.g.][and references
  therein]{popsyn-LowMetallicityImpact-Chris2008,popsyn-LIGO-SFR-2008,gwastro-EventPopsynPaper-2016}.
% POINT: 
%   - final BH spin, mass can change number favored
%   - of course
Gravitational wave detectors are also far more sensitive to  massive compact binaries, \sout{as}  \jillianremark{ which?} are  preferentially  formed in low metallicity
environments \citep{PSellipticals,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.  As a result, low metallicity
environments can be overwhelmingly efficient factories for detectable black hole binaries
\citep{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,gwastro-EventPopsynPaper-2016}.  
%
For this reason, our estimates for compact binary coalescence rates must account for how often  different star-forming
conditions occur;  how often compact binaries that can coalesce now \jillianremark{\sout{can}}  derive from each environment; and how often LIGO will detect compact
binaries with different masses, all other things being equal.

\begin{widetext}
% POINT:  Model
To characterize how much more likely LIGO will detect coalescing binaries with different masses, we use a common and
naive estimate for the volume to which advanced LIGO is sensitive \citep[see,e.g.,][]{PSellipticals}:\footnote{For
  simplicity, in this calculation we neglect the effects of cosmology; strong field coalescence; and black hole spin;
  see \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, \cite{AstroPaper}, or \cite{RatesPaper} for more details.}
\begin{eqnarray}
V = \frac{4\pi}{3} [445 \unit{Mpc}]^3 \int p(m_1,m_2|Z) dm_1 dm_2 [ (\mc/1.2 M_\odot)^{5/6}]^3
\end{eqnarray}
where $\mc\equiv (m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$.   
This expression depends explicitly on an assumed \jillianremark{\sout{and}} metallicity-dependent mass distribution for compact object
mergers, through the characteristic chirp mass $\mc_{*}(Z)\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
  M_\odot)^{15/6}]^{5/16}$ .  We calibrate our metallicity-dependent mass distributions to metallicity-dependent binary
evolution calculations presented in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} and
\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; see, e.g., their Table 1 and Figures 5-7.    For neutron
stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.  For BH-NS binaries, we adopt a
highly simplified model: the black hole masses are uniformly \editremark{fixme?} drawn from $5 M_\odot$ to the maximum 
black hole mass $M_{max}(Z)$ allowed by
\emph{isolated} stellar evolution, as reported in prior work \citep[see,e.g.][and references
  therein]{gwastro-EventPopsynPaper-2016}.  In agreement with much more detailed prior work \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, this simplified model yields typical chirp masses for BH-NS binaries that
vary slightly as $Z/Z_\odot$ decreases, from a lower limit of $3 M_\odot$ near solar metallicity to an upper limit of
$4.3 M_\odot$ in low-metallicity environments.  Finally, for binary black holes, we assume  comparable-mass binaries
form ($m_1=m_2$), with the distribution of component masses chosen to be $\propto m_1^{-p}$ 
 with $p=2$ between $3 M_\odot$ and $M_{max}(Z)$ and zero otherwise \jillianremark{(hold on, p=0 otherwise or masses $ \propto 0$ otherwise?)}; see, e.g.,
\cite{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.    For binary black holes, this means  the
detection-weighted mass distribution [$\propto p(m_1,m_2)
\mc^{15/6}$] depends weakly on mass [$ p(m_1,m_2)
\mc^{15/6} \propto m_1^{-0.5} \delta(m_1-m_2)$.  In our simple model, the total  and chirp mass
distributions   are qualitatively consistent with detailed  binary evolution calculations \citep{popsyn-LowMetallicityImpact2b-StarTrackRevised-2013}.

@@

% POINT:  Model
To characterize the frequency of different star-forming conditions, we use our cosmological simulations of Milky Way-like galaxies, which provide each galaxy's star formation rate
$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$ over time.

% POINT: 
To characterize how often compact binaries form and coalesce, we use the ansatz adopted in \abbrvPSellipticals{} and
\abbrvPSgrb{}: for a star-forming parcel of mass $\Delta M$ the number of binaries born at time $0$ which
are coalescing now is $\lambda \Delta M dP/dt$, where $\lambda$ is an overall efficiency per unit mass and $P(<t|Z)$ is
a metallicity-dependent delay time distribution.\footnote{For simplicity, we assume the mass and delay time
  distributions are uncorrelated.  Figure A9 in \abbrvPSgrb{} shows this approximation, while not strictly true, is an
  excellent approximation for merging BH-BH binaries at solar metallicity.  }
    In this paper we only investigate the relative contribution of
different star-forming environments, not the overall normalization \jillianremark{(why doesn't the absolute value matter?)}, so the overall scale of $\lambda$ is irrelevant.  
However, to account for the strong tendency of low-metallicity star-forming regions to produce many binary compact
objects, we adopt a power law
\begin{eqnarray}
\label{eq:LambdaVersusZModel}
\lambda(Z) &=& \lambda_o \text{min}[(Z/Z_\odot)^{-a}, F_{max}] 
\end{eqnarray}
with $a\in [0,3]$ and $F_{max}<10^3$
%$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
 (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).  For the purposes of illustration, we adopt a  concrete scale
factor  $
\lambda_0 = 10^{-3}/M_\odot $,  a typical value suitable for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
%
For binaries containing neutron stars, for simplicity and without loss of generality we adopt the universal delay time distribution
%% Finally, we parameterize the delay time distribution by  either
%% \begin{eqnarray}
%% P_t(<t) &=& \begin{cases}
%% 0 & t<10 \unit{Myr} \\
%% (t/13\unit{Gyr})^{b}& t \in [10\unit{Myr},t_H]
%% \end{cases} 
%% \end{eqnarray}
%% with $b> 0$ or as the special case
\begin{eqnarray}
\frac{dP_t(<t)}{dt} =  \begin{cases}
0 & t<10 \unit{Myr} \\
\frac{1}{t \ln (13 \unit{Gyr}/10\unit{Myr})} & t \in [10\unit{Myr},13\unit{Gyr}]
\end{cases} 
\end{eqnarray}
\abbrvPSgrb{} and \abbrvPSellipticals{} show this distribution is reasonable approximations to compact binary delay
time distributions.\footnote{Simulations suggest the delay time distribution varies from model to model and with mass.
  These variations have less impact on our results than the evolving metallicity distribution of star forming gas.}
%
For suitable choices of parameter, our phenomenological response function is qualitatively consistent with the results of detailed simulations of binary
evolution  \citep{2010ApJ...715L.138B,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,popsyn-LowMetallicityImpact2-StarTrackRevised-2012}.

For binary black holes formed near solar metallicity, the delay time distribution can favor long delays between birth
and merger, as demonstrated in Figures 9 and 10 of \abbrvPSellipticals{}.  [Figure 2 of  \cite{2016arXiv160508783L} is
  an extreme example of this well-known trend.]  In practice, however, binary black holes produced near solar
metallicity correspond to a relatively small proportion of the overall population; we therefore neglect this
effect\footnote{may want to change}.
